Real-Time Scheduling Algorithms and Battery Consumption of Mobile Devices

### 2017-05-04 paper-RMDON.tex
resultados, related work y otras cosas

A real-time operating system has a well-specified maximum time for each action that it performs to support applications with precise timing needs. Systems that can guarantee these maximum times are called hard real-time systems. Those that meet these times most of the time are called soft real-time systems. Deploying an airbag in response to a sensor being actuated is a case where you would want a hard real-time system. Decoding video frames is an example of where a soft real-time system will suffice

@@

@@

\section{Representative Algorithms} \label{hard-rt-algs}

%Table 2 summarizes the DVS algorithms selected for the comparative  study.

Nine  InterDVS  algorithms  are chosen, two of which are based on the RM scheduling policy, while the other seven algorithms are based on the EDF scheduling policy. Two algorithms were selected for IntraDVS, one from path-based IntraDVS algorithms, and the other from stochastic methods.

%In these selected DVS algorithms, one or sometimes more than one slack estimation methods explained in the previous section were used.

%In \texttt{lppsEDF} and \texttt{lppsRM} which were proposed by Shin \emph{et. al.} in  [18], slack time of a task is estimated using the maximum constant speed and Stretching-to-NTA methods. 
%
%The \texttt{ccRM} algorithm proposed by Pillai \emph{et. al.} [14]  is similar to \texttt{lppsRM} in the sense that it uses both the maximum constant speed and the Stretching-to-NTA methods. However, while \texttt{lppsRM} can adjust the voltage and clock speed only when a single task is active, \texttt{ccRM} extends the stretching to NTA method to the case where multiple tasks are active.

@@

@@

\section{Results}
In \cite{kim-2} a performance comparison of most of the algorithms presented in section \ref{hard-rt-algs} was made using a simulation environment named SimDVS. It is argued that the energy efficiency of InterDVS algorithms depends significantly of slack estimation and the appropriateness of slack distribution. The following highlights the results obtained when evaluating InterDVS algorithms.

@@

\textbf{==> Aqui Poner resultados de \texttt{darEDF} <==}

@@

\section{Related Work}
\begin{itemize}
    \item otros algoritmos para hard-time (lfpsEDF por ejemplo)
    \item scheduling en mobile devices basado en offloading
\end{itemize}

\section{Conclusions}

@@

@@

>>>>

A real-time operating system has a well-specified maximum time for each action that it performs to support applications with precise timing needs. Systems that can guarantee these maximum times are called hard real-time systems. Those that meet these times most of the time are called soft real-time systems. Deploying an airbag in response to a sensor being actuated is a case where you would want a hard real-time system. On-line transaction systems, airline reservation systems and decoding video frames are examples of where a soft real-time system can be used.

@@

\section{Hard Real-Time versus Soft Real-Time Systems}
The following are the major differences between hard and soft real-time systems according to \cite{juvva}. 
\paragraph{Response time requirements} on hard real-time systems are in the order of milliseconds or less and can result in a catastrophe if not met. In contrast, the response time requirements of soft real-time systems are higher and not very strict.

\paragraph{Peak-load performance} in a hard real-time system, must be predictable and should not violate the predefined deadlines. In a soft real-time system, a degraded operation in a rarely occurring peak load can be tolerated.

\paragraph{Safety} a hard real-time system must remain synchronous with the state of the environment in all cases. On the other hand soft real-time systems will slow down their response time if the load is very high. Hard real-time systems are often safety critical.

\paragraph{Size of data files} hard real-time systems have small data files and real-time databases. Temporal accuracy is often the concern here. Soft real-time systems for example, on-line reservation systems have larger databases and require long-term integrity of real-time systems. If an error occurs in a soft real-time system, the computation is rolled back to a previously established checkpoint to initiate a recovery action. In hard real-time systems, roll-back/recovery is of limited use.

@@

\section{Representative Algorithms} \label{hard-rt-algs}
Many DVS algorithms have been proposed or developed, especially for hard real-time systems. Since lowering the supply voltage also decreases the maximum achievable clock speed, various DVS algorithms for hard real-time systems have the goal of reducing supply voltage dynamically to the lowest possible level while satisfying the tasks' timing constraints\cite{kim-2}. The following is a representative list of DVS algorithms that have been proposed for addressing energy efficiency on mobile devices: two of which are based on the RM scheduling policy, while the other algorithms are based on the EDF scheduling policy, the two most widely used real-time system models\cite{w-s-liu}. Two algorithms were selected for IntraDVS, one from path-based IntraDVS algorithms, and the other from stochastic methods.

@@

\textbf{==> TENTATIVO: hablar de lpfpsEDF que viene en Power Concious...}

@@

\section{Results}
In \cite{kim-2} a performance comparison of most of the algorithms presented in section \ref{hard-rt-algs} was made using a simulation environment named SimDVS. This work is relevant because it is argued that although each DVS algorithm is shown to be quite effective in reducing the energy/power consumption of a target system under its own experimental scenarios, these DVS algorithms have not been quantitatively evaluated under a unified framework, making it a difficult task for low-power embedded system developers to select an appropriate DVS algorithm for a given application/system.

%Although each DVS algorithm is shown to be quite effective in reducing the energy/power consumption of a target system under its own experimental scenarios,  these recent DVS algorithms have not been quantitatively evaluated under a unified framework, making it a difficult task for low-power embedded system developers to select an appropriate DVS  algorithm for  a  given application/system. A quantitative analysis of the energy-efficiency is particularly important because most of these DVS algorithms are based on both static and dynamic slack analysis techniques whose performance is difficult to predict analytically.  In addition, their energy  efficiency  fluctuate  significantly  depending  on  the workload variations, task set characterizations, and execution paths taken, further requiring a quantitative comparison study.

%It is argued that the energy efficiency of InterDVS algorithms depends significantly of slack estimation and the appropriateness of slack distribution. The following highlights the results obtained when evaluating InterDVS algorithms.

@@

Regarding the results of \texttt{darEDF} discussed in \cite{zhuo-chakrabarti}, the comparison with competing algorithms such as \texttt{lppsEDF} and \texttt{lpSEH} revelead that \texttt{darEDF} has the best performance both with respect to charge consumption and energy consumption, besides a lower runtime complexity than \texttt{lpSEH} wich has been proven to have close optimal energy saving according to \cite{kim-2}.

@@

\section{Related Work}
Although this work is focused in hard real-time scheduling algorithms, CPU scheduling and energy/power efficiency of soft real-time systems and mobile devices has been addressed as well. In \cite{yuan-nahrstedt-1} a framework to integrate DVS into soft real-time scheduling for open mobile systems is presented. Its goal is to achieve energy saving DVS while preserinf resource guarantees of soft real-time scheduling. In \cite{yuan-nahrstedt} an enery efficient soft real-time CPU scheduler intended for mobile multimedia systems named \emph{GRACE-OS} is presented.

In \cite{kim-2} hybrid methods are discussed as well. By using this methods researchers try to answer quest of whether hybrid DVS algorithms will perform better than pure InterDVS or pure IntraDVS. The study indicates that the performance of a HybridDVS algorithm can be better than a pure IntraDVS algorithm or a pure InterDVS algorithm. However, the differences in energy efficiency depend on the characteristics of both the IntraDVS and the InterDVS components used in the HybridDVS algorithm.

Another popular technique to reduce energy consumption of mobile devices is computation offloading in which an application reduce energy consumption by delegating code execution to other devices. Traditionally, computations are offloaded to remote servers. Selection of a proper offloading strategy can reduce power consumption and simultaneously enhance performance for mobile device. Following this technique, in \cite{quian-andresen} a computation offloading system for mobile devices named \emph{Jade} is presented. \emph{Jade} implements a multi-level task scheduling algorithm that enables energy and performance-aware task scheduling. It is built for mobile devices running Android operative system and it minimizes energy consumption of mobile devices through fine-grained computation offloading to the cloud. The algorithm (1) incorporates server status, (2) balances the workload between servers, and (3) offloads tasks to the most appropiate server according to the energy and computing demand of the task.

In \cite{kwon-tilevich} another offloading approach that combines the advantages of particioning mobile applications and in dynamically adaptin mobile execution targets in response to fluctuations in network conditions. The proposed approach is realized as the following two technical solutions: (1) a multitarget offloading program transformation that automatically rewrites a centralized program into a distributed program, whose local/remote distribution is determined dynamically at runtime; (2) a runtime system that determines the required local/remote distribution of the resulting distributed program based on the current execution environment. Combining these two solutions can effectively reduce the amount of energy consumed by mobile applications without having to change their source code by hand, thus optimizing them behind the scenes.

%Since in these systems resource demands differs from the ones presented in hard real-time systems, performance improvements are approached depending of the application quality of service (QoS) that is being intended to be improved, for instance disks access, multimedia or network utilization. 
%
%\begin{itemize}
%    \item otros algoritmos para hard-time (lfpsEDF por ejemplo)
%    \item scheduling en mobile devices basado en offloading
%\end{itemize}

\section{Conclusions}
In this paper, real-time scheduling principles and algorithms and their impact on mobile device energy/power consumption are discussed.

@@

\bibitem{juvva}K.~Juvva. \emph{Real-Time Systems}. Carnegie Mellon University. 18-849b Dependable Embedded Systems. Spring 1998. Available at \url{https://users.ece.cmu.edu/koopman/des_s99/real_time}

@@

\bibitem{yuan-nahrstedt-1}W.~Yuan and K.~Nahrstedt, \emph{Integration of Dynamic Voltage Scaling and Soft Real-Time Scheduling for Open Mobile Systems}, In Proceedings of the 12th international workshop on Network and operating systems support for digital audio and video (NOSSDAV '02). ACM, New York, NY, USA, 105-114. 2002.
